RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-28 discussion.tex
yes

{\bf Discussion.} Annotation and commenting was another central goal
of our prototype, and is provided in our human interface.
An interesting question is, to what extent should application users
be able to make annotations and operate similar tools in published
notebooks without coding and being exposed to the hackers's view?
Our prototype has not addressed this problem yet.

>>>>

{\bf Discussion.} Annotation and commenting was another central goal.
Commenting is supported through github, but our hackers found it
awkward and did not exercise it as much as we expected.
making it a bit awkward and
not as widely used as we hoped.  More elaborate annotation was not
implemented, and remains as future work.
An interesting question is, to what extent should application users
be able to make annotations and operate similar tools in published
notebooks without coding and being exposed to the hackers's view?
Our prototype has not addressed this problem yet.
